---
title: "ADA analysis"
output:
  pdf_document: default
  html_document: default
date: "2023-03-11"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

We will focus on the data from the experiment task. 

## Variables' Description

- player_code: unique ID for each participant (in our case, each participant group)
- round: the round number in the experiment, 1-10
- trmt_accur: one of the two main experiment factors. High Accuracy: participants worked with 80% accuracy AI, Low Accuracy:  participants worked with 60% accuracy AI, Baseline: participants worked on their own

- typeI: number of type I errors each participant made in each round (initial/final stage)
- typeII: number of type II errors each participant made in each round (initial/final stage)
- ai_typeI: number of type I errors the AI (computer model) made in each round
- ai_typeII: number of type II errors the AI (computer model) made in each round

- confidence_*_total : total confidence ratings each participant gave
- confidence_*_avg : average confidence ratings each participant gave[total confidence divided by number of completed decisions]


```{r}
## Load Data
df <- read.csv("type_error.csv",
  header = T,
  stringsAsFactors = FALSE)
df <- na.omit(df)

summary(df)

## Compute participant-level metrics (aggregated over 10 rounds)
## Let's first focus on Type I & Type II errors

library(dplyr)

perf_msrs <- c(
  "typeI", "typeI_rate", 
  "typeII", "typeII_rate", 
  "ai_typeI", "aitypeI_rate", 
  "ai_typeII", "aitypeII_rate",
  "arg_confidence_level")

library("summarytools") 

## Summary Stats overall - all conditions
df_describe <- dfSummary(df[perf_msrs])

filename <- "descriptives_data.html"
view(df_describe, file = filename)

## Summary Stats - each condition
df_describe_conds <- dfSummary(df_describe)

name <- "descriptives_data_conds.html"

view(df_describe_conds, file = name) # should run in console if output missing conditions

```

```{r}
### can also use hist() to look at distribution shape of your DVs for each condition
RA <- df[df$treatment== "RA", ]

Baseline <- df[df$treatment == "Baseline", ]

hist(RA$typeI_rate)
hist(Baseline$typeI_rate)

```

```{r}
## Comparing between 2 conditions
## Kruskal Wallis Test 
## kruskal.test(DV ~ treatment_factor, data = data)

kruskal.test(
  typeI_rate ~ treatment,
  data = df
      )
```
```{r}
#Mann-Whitney U testing 
control_data <- df$typeI_rate[df$treatment == "Baseline"]

# Subset the data for the treatment group
treatment_data <- df$typeI_rate[df$treatment == "RA"]

# Perform the Mann-Whitney U test
result <- wilcox.test(control_data, treatment_data)

```

```{r}
## Comparing between 2 conditions
## ANOVA
## anova <- aov(DV ~ treatment_factor, data = data)
## summary(anova)

test <- aov(
   typeI_rate ~ treatment,
  data = df)
summary(test)
#结果没有显著不同，也就是两条件之间无显著差距
```

```{r}

## Visualization

library(ggplot2)
library(ggpubr) ## a very useful package that provides some easy-to-use functions for creating and customizing 'ggplot2'-based publication ready plots.

df$treatment <- as.factor(df$treatment)

barplot <- ggbarplot( ## ggbarplot() requires "ggpubr" package
  data = df, 
  x = "treatment", xlab = "Condition",
  y = "typeI_rate", 
  ylab = "Type I Rate",
  fill = "treatment", ## color for each condition
  add = "mean_se", ## includes standard error bar
  label = TRUE, ## includes summary stats on chart
  label.pos = "in", 
  lab.nb.digits = 2) + ## round displayed stats to 2 decimal places
    stat_compare_means(method = "kruskal.test") + ## displays kruskal wallis results on chart 
    theme(text = element_text(size = 12, face = "bold"),
          axis.text=element_text(size = 12),
          legend.position = "none")

ggsave(plot = barplot, width = 10, height = 8, dpi = 300,
           filename =  "barplot_typeI_rate.jpeg")
```

Now start the analysis of TypeII_rate

```{r}
### can also use hist() to look at distribution shape of your DVs for each condition
hist(RA$typeII_rate)
hist(Baseline$typeII_rate)

```

```{r}
## Comparing between 2 conditions
## Kruskal Wallis Test 
## kruskal.test(DV ~ treatment_factor, data = data)

kruskal.test(
  typeII_rate ~ treatment,
  data = df
      )
```
```{r}
#Mann-Whitney U testing 
control_data2 <- df$typeII_rate[df$treatment == "Baseline"]

# Subset the data for the treatment group
treatment_data2 <- df$typeII_rate[df$treatment == "RA"]

# Perform the Mann-Whitney U test
result2 <- wilcox.test(control_data2, treatment_data2)

```

```{r}
## Comparing between 2 conditions
## ANOVA
## anova <- aov(DV ~ treatment_factor, data = data)
## summary(anova)

test2 <- aov(
   typeII_rate ~ treatment,
  data = df)
summary(test2)
#结果没有显著不同，也就是两条件之间无显著差距
```

```{r}

## Visualization

barplot2 <- ggbarplot( ## ggbarplot() requires "ggpubr" package
  data = df, 
  x = "treatment", xlab = "Condition",
  y = "typeII_rate", 
  ylab = "Type II Rate",
  fill = "treatment", ## color for each condition
  add = "mean_se", ## includes standard error bar
  label = TRUE, ## includes summary stats on chart
  label.pos = "in", 
  lab.nb.digits = 2) + ## round displayed stats to 2 decimal places
    stat_compare_means(method = "kruskal.test") + ## displays kruskal wallis results on chart 
    theme(text = element_text(size = 12, face = "bold"),
          axis.text=element_text(size = 12),
          legend.position = "none")

ggsave(plot = barplot2, width = 10, height = 8, dpi = 300,
           filename =  "barplot_typeII_rate.jpeg")
```

Now we move to the analysis of average confidence level between RA and Baseline

```{r}
### can also use hist() to look at distribution shape of average confidence level for each condition

hist(RA$arg_confidence_level)
hist(Baseline$arg_confidence_level)

```

```{r}
## Comparing between 2 conditions
## Kruskal Wallis Test 
## kruskal.test(DV ~ treatment_factor, data = data)

kruskal.test(
  arg_confidence_level ~ treatment,
  data = df
      )
```
```{r}
#Mann-Whitney U testing 
control_data3 <- df$arg_confidence_level[df$treatment == "Baseline"]

# Subset the data for the treatment group
treatment_data3 <- df$arg_confidence_level[df$treatment == "RA"]

# Perform the Mann-Whitney U test
result3 <- wilcox.test(control_data3, treatment_data3)

```

```{r}
## Comparing between 2 conditions
## ANOVA
## anova <- aov(DV ~ treatment_factor, data = data)
## summary(anova)

test3 <- aov(
   arg_confidence_level ~ treatment,
  data = df)
summary(test3)
#结果没有显著不同，也就是两条件之间无显著差距
```

```{r}

## Visualization

barplot3 <- ggbarplot( ## ggbarplot() requires "ggpubr" package
  data = df, 
  x = "treatment", xlab = "Condition",
  y = "arg_confidence_level", 
  ylab = "average confidence level",
  fill = "treatment", ## color for each condition
  add = "mean_se", ## includes standard error bar
  label = TRUE, ## includes summary stats on chart
  label.pos = "in", 
  lab.nb.digits = 2) + ## round displayed stats to 2 decimal places
    stat_compare_means(method = "kruskal.test") + ## displays kruskal wallis results on chart 
    theme(text = element_text(size = 12, face = "bold"),
          axis.text=element_text(size = 12),
          legend.position = "none")

ggsave(plot = barplot3, width = 10, height = 8, dpi = 300,
           filename =  "barplot_arg_confidence_level.jpeg")
```

```{r}
df <- read.csv("Result.csv",
header = T,
stringsAsFactors = FALSE)

## Summary Statistics

df_descr <- dfSummary(df) ## requires "summarytools" package
filename <- "descriptives.html"
view(df_descr, file = filename)
```

```{r}
## Comparing between 2 conditions
## Kruskal Wallis Test
## kruskal.test(DV ~ treatment_factor, data = data)

kruskal.test(
AllLoan ~ Condition,
data = df
)
```